Reasoning About a Machine with Local Capabilities

### 2018-04-28 toplas/paper.tex
Added the following definitions to appendix in paper: nsubsim, erasure, and acvtiveReg
Added implementation of scall figure and macros used by scall to appendix

The technical appendix~\citep{technical_appendix} contains detailed descriptions
of all the macros.
\itoplassug{Suggestion: Add the call implementation (and possibly other macros?) in the above?}
\end{toplas}

@@

%% Appendix
% \appendix
% \section{Appendix}

% Text of appendix \ldots

>>>>

The technical appendix~\citep{technical_appendix} contains detailed descriptions
of all the macros.
\itoplassug{Suggestion: Add the call implementation (and possibly other macros?) in the above?}

\begin{figure}[htb]
  \centering
\begin{lstlisting}
// push private registers to the stack
  push $r_{\var{priv},1}$
  ...
  push $r_{\var{priv},n}$
// push restoration code to the stack
  push $\encode(i_1)$
  ...
  push $\encode(i_4)$
// push old pc to the stack
  move r_t1 pc
  lea r_t1 $\var{ofc}$ 
  push r_t1
// push stack pointer to the stack
  push r_stk
// set up protected return pointer
  move r_0 r_stk
  lea r_0 $\var{ofc_\var{act}}$ // -5 is the offset to the first instruction of the activation code
  restrict r_0 $\encodePermPair((\local,\entry))$
// restrict stack capability to unused part
  geta r_t1 r_stk
  plus r_t1 r_t1 1
  getb r_t2 r_stk
  subseg r_stk r_t1 r_t2
// clear unused part of the stack
  mclear r_stk
// clear non-argument registers
  rclear $R$
  jmp r
after:
// pop the restore code
  pop r_t1
  pop r_t1
  pop r_t1
  pop r_t1
// pop the private state into approriate registers
  pop $r_{\var{priv},1}$
  ...
  pop $r_{\var{priv},n}$
\end{lstlisting}
  \caption{Implementation of \texttt{scall} $r(r_{\var{args},1},\dots,
    r_{\var{args},m},r_{\var{priv},1},\dots, r_{\var{priv},n})$. The restoration
  code is given in \figurename~\ref{fig:scall-rest-code}. The variable
  $\var{ofc}$ is the offset to the label after, and $\var{ofc_\var{act}} =
  -5$ which is the offset to the first instruction of the activation record. The
set $R = \RegName \setminus
\{\texttt{pc},\texttt{r\_stk},\texttt{r\_0},r,r_{\var{args},1},\dots,r_{\var{args},m}\}$.}
  \label{fig:scall-impl}
\end{figure}
\begin{figure}[htb]
  \centering
  \begin{lstlisting}
 $i_1$ = move r_t1 pc
 $i_2$ = lea r_t1 $\var{ofc}$
 $i_3$ = load r_stk r_t1
 $i_4$ = pop pc
\end{lstlisting}
  \caption{The restoration code used in \texttt{scall}. The variable $\var{ofc}$ is 5
    which is the offset to the address where the old stack pointer is stored on
    the stack.} 
  \label{fig:scall-rest-code}
\end{figure}

@@

%% Appendix
\appendix
\section{Appendix}
\subsection{Logical relation}
\label{app:logical-relation}
% Text of appendix \ldots
\textbf{$n$-subset simulation}
\begin{mathpar}
  \inferrule{(s,\phi_\pub,\phi) = (s',\phi_\pub',\phi') \\
    \forall \hat{W} \ldotp H \; s \; \hat{W} \nsubeq H' \; s' \; \hat{W} }
  { (v,s,\phi_\pub,\phi,H) \nsubsim (v',s',\phi_\pub',\phi',H')}
\end{mathpar}
\textbf{Erasure}
\begin{align*}
  \lfloor W \rfloor_S \defeq \lambda r \ldotp 
  \begin{cases}
    W(r) & W(r).v \in S\\
    \bot & \text{otherwise}
  \end{cases}
\end{align*}
\textbf{Active region projection}
\begin{align*}
  \activeReg{} & : \Worlds \fun 2^\RegionNames \\
  \activeReg{W} & \defeq \dom(\erase{W}{\perma,\temp})
\end{align*}

\subsection{Macros}
Implementation of the macros used in \texttt{scall}. Implementations of the
macros not presented here can be found in the technical
appendix~\citep{technical_appendix}.\\
\label{app:macros}
\texttt{push $r$}
\begin{lstlisting}
  lea r_stk 1
  store r_stk r
\end{lstlisting}
\texttt{pop $r$}
\begin{lstlisting}
  load r r_stk
  minus r_t1 0 1
  lea r_stk r_t1
\end{lstlisting}
\texttt{rclear $r_1,\dots, r_n$}
\begin{lstlisting}
move $r_1$ 0
move $r_2$ 0
$\dots$
move $r_n$ 0
\end{lstlisting}
\texttt{mclear $r$}
\begin{lstlisting}
        move r_t $r$
        getb r_t1 r_t
        geta r_t2 r_t
        minus r_t2 r_t1 r_t2
        lea r_t r_t2
        gete r_t2
        minus r_t1 r_t2 r_t1
        plus r_t1 r_t1 1
        move r_t2 pc
        lea r_t2 $\var{ofc}_\var{end}$ 
        move r_t3 pc
        lea r_t3 $\var{ofc}_\var{iter}$
iter:
        jnz r_t2 r_t1
        store r_t 0
        lea r_t 1
        plus r_t1 r_t1 1
        jmp r_t3
end:
        move r_t 0
        move r_t1 0
        move r_t2 0
        move r_t3 0
\end{lstlisting}
Where $\var{ofc}_\var{end}$ and $\var{ofc}_\var{iter}$ are the offsets to the
label \texttt{end} % 9?
and \texttt{iter}, % 2?
respectively.
